Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Small update to get SD for k

# Summary of the cleaned data for 218 traits
  range(meta_clean$male_N)
  range(meta_clean$female_N)
  range(meta_clean$lnCVR_I2)
  range(meta_clean$lnVR_I2)
  range(meta_clean$lnRR_I2)
  range(meta_clean$k)
  mean(meta_clean$mean_male_N)
  range(meta_clean$min_male_N)
  median(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N) / sqrt(length(meta_clean$mean_male_N))
  mean(meta_clean$mean_female_N)
  median(meta_clean$mean_female_N)
  range(meta_clean$min_female_N)
  sd(meta_clean$mean_female_N)
  sd(meta_clean$mean_female_N) / sqrt(length(meta_clean$mean_female_N))

>>>>

# Summary of the cleaned data for 218 traits
  sd(meta_clean$k)
  range(meta_clean$male_N)
  range(meta_clean$female_N)
  range(meta_clean$lnCVR_I2)
  range(meta_clean$lnVR_I2)
  range(meta_clean$lnRR_I2)
  range(meta_clean$k)
  mean(meta_clean$mean_male_N)
  range(meta_clean$min_male_N)
  median(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N)
  sd(meta_clean$mean_male_N) / sqrt(length(meta_clean$mean_male_N))
  mean(meta_clean$mean_female_N)
  median(meta_clean$mean_female_N)
  range(meta_clean$min_female_N)
  sd(meta_clean$mean_female_N)
  sd(meta_clean$mean_female_N) / sqrt(length(meta_clean$mean_female_N))
